---
title: "Code to Generate Word Cloud of Library Strategic Plans"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Preliminaries

Load the following libraries: 

```{r, message=FALSE, warning=FALSE}
# Load relevant libraries
library(pdftools)
library(tm)
library(SnowballC)
library(wordcloud)
library(tidyverse)
library(knitr)
```

The following script assumes that all of the strategic plans listed in the strategic plans spreadsheet (located in the repository's [data](https://github.com/aranganath24/clirproject/tree/main/data) folder) are downloaded as PDFs to your R working directory. 

## Create vector of plan document names

In the following, we make a vector of the names of strategic plan file names (all plans are stored as PDFs in the working directory), and assign this vector to an object named ```files```.

```{r, echo=-1, message=FALSE, warning=FALSE}
setwd("~/Documents/strategic_plans/update")
# Make a vector of the names of the PDF files (i.e. plan documents) in working directory
files<-list.files(pattern="pdf$")
```

## Make corpus and term document matrix

We will now use the vector of plan document names (```files```) to make a text corpus that is based on the underlying text of the strategic plans; this corpus is assigned to an object named ```corpus_plans```:

```{r, message=FALSE, warning=FALSE}
# Make corpus based on strategic plan documents
corpus_plans<-Corpus(URISource(files),readerControl = list(reader=readPDF))
```

Now, we use the corpus as an argument in the ```TermDocumentMatrix``` function to make a term document matrix derived from the corpus. This term document matrix is assigned to an object named ```plans.tdm```

```{r, message=FALSE, warning=FALSE}
# Make term document matrix based on corpus_plans object
plans.tdm <- as.matrix(TermDocumentMatrix(corpus_plans, 
                                control = 
                                  list(removePunctuation = TRUE,
                                       stopwords = TRUE,
                                       tolower = TRUE,
                                       stemming = FALSE,
                                       removeNumbers = TRUE,
                                       bounds = list(global = c(3, Inf)))))  
```

## The frequency of "commons" in the plan corpus

How many times does the word "commons" appear in the corpus of strategic plans? To find out, we extract a vector that sums up the number of times various words appear in the corpus using the ```rowSums``` function, and assign this vector to an object called ```words```; we then create a data frame based on ```words```, with one column (named "word") containing the various words in the corpus, and the other column (named "freq") containing information on how many times the associated word appears in the corpus. We then extract the rows with the words "commons" and "library" (to serve as a reference point) to see how many times they appear in the corpus. 

```{r}
# Extract vector containing information on word frequencies
words <- sort(rowSums(plans.tdm), decreasing=TRUE)
# Create a data frame based on the information in "words"
df <- data.frame(word = names(words),freq=words)
# Find the frequency of "commons" and "library" in the corpus 
df %>% filter(word=="commons"|word=="library") %>% remove_rownames()
```

## Generate word cloud 

Finally, we use the "word" and "freq" columns from the ```df``` object created above to generate a word cloud of the most frequently recurring words in the strategic plan corpus:

```{r, message=FALSE, warning=FALSE}
# Set seed for reproducibility
set.seed(1234)
# Generate word cloud
wordcloud(words = df$word, freq = df$freq, min.freq = 50, max.words=90, random.order=FALSE, rot.per=0.35, colors=brewer.pal(8, "Dark2"))
```

